\huge Tor's Usability for Censorship Circumvention

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Put labels after captions in appenx figures.
Use session rather than full runid in participant identification.

Only connected directly (8/23): 
\begin{itemize}
\item E2-NEW-X21-20160323-133257 
\item E2-OLD-X04-20160330-181928
\item E2-OLD-X10-20160331-153028
\item E3-NEW-X05-20160324-132535
\item E3-NEW-X17-20160323-133002
\item E3-OLD-X06-20160328-132053
\item E3-OLD-X06-20160330-161525 
\item E3-OLD-X12-20160330-182011
\end{itemize}

Didn't know what to do next (6/23): 
\begin{itemize}
\item E3-NEW-X11-20160330-161511
\item E3-NEW-X11-20160331-174655
\item E3-NEW-X23-20160323-133346
\item E3-OLD-X06-20160331-174650
\item E3-OLD-X12-20160331-153055
\item E3-OLD-X30-20160328-134412
\end{itemize}

Thought that they needed a proxy (6/23): 
\begin{itemize}
\item E2-OLD-X10-20160328-132828
\item E3-NEW-X18-20160330-170145
\item E3-NEW-X17-20160328-160037
\item E3-OLD-X06-20160325-175101
\item E3-OLD-X06-20160330-181926
\item E3-OLD-X24-20160328-155926
\end{itemize}

Used the bridges auto-responder incorrectly (3/23): 
\begin{itemize}
\item E3-NEW-X23-20160328-155924 (Fig.~\ref{autoresponder1})
\item E3-OLD-X12-20160325-140813 (Fig.~\ref{autoresponder2})
\item E3-OLD-X24-20160328-133857 (Fig.~\ref{autoresponder3})
\end{itemize}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
\caption{The message that E3-NEW-X23-20160328-155924 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
\label{autoresponder1}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
\caption{The message that E3-OLD-X12-20160325-140813 accidentally sent to the helpdesk rather than the bridge auto-responder. The participant should have used the address bridges@torproject.org, not help@rt.torproject.org. Since the helpdesk address is not an auto-responder, there was no reply.}
\label{autoresponder2}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
\caption{The message that E3-OLD-X24-20160328-133857 sent to the bridge auto-responder. A correct message is a ``get bridges'' in the body of the message, with any non-empty subject. Since this request was incorrectly formatted, there was no reply.}
\label{autoresponder3}
\end{figure}

@@

Participants that downloaded Tor (5/124): 
\begin{itemize}
\item E1-OLD-X32-20160328-134531(Fig.~\ref{mirror})
\item E2-NEW-X21-20160323-133257 (Fig.~\ref{techspot})
\item E2-OLD-X10-20160323-132505 (Fig.~\ref{downloadio})
\item E2-OLD-X28-20160328-134111 (Fig.~\ref{driverupdate})
\item E3-NEW-X11-20160330-161511 (Fig.~\ref{softsonic})
\end{itemize}

Sources of downloads: 
\begin{itemize}
\item {\bfseries techspot.com -> 1download.io}: the ad firefox yahoo ad result for ``tor browser downloads.'' 
\item {\bfseries driverupdate.net}: the 5th chrome google search result for ``tor browser download.'' 
\item {\bfseries www.torservers.net/mirrors}: the first chrome google search result for ``tor browser mirror.''
\item {\bfseries techspot.com}: the 5th chrome google search result for ``tor browser download.''
\item {\bfseries softsonic.com}: the 2nd firefox yahoo search result for ``tor browser.''
\end{itemize}

\begin{figure}[h]
\label{downloadio}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
\caption{X10-20160323-132505 attempted downloaded Tor Browser from TechSpot.com, but clicked on one 
a download link which was not from TechSpot.com. The download was from 1download.io, a suspicious source.}
\end{figure}

\begin{figure}[h]
\label{driverupdate}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
\caption{X28-20160328-134111 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
participant dutifully does before running the Tor Browser executable.}
\end{figure}

\begin{figure}[h]
\label{mirror}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
\caption{X32-20160328-134531 downloaded Tor Browser from a legitimate Tor Browser mirror,www.torservers.net/mirrors.}
\end{figure}

\begin{figure}[h]
\label{techspot}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
\caption{E2-NEW-X21-20160323-133257 downloaded Tor Browser from TechSpot, clicking on the download link from 
TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
\end{figure}

\begin{figure}[h]
\label{softsonic}
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
\caption{E3-NEW-X11-20160330-161511 downloaded Tor Browser from Softsonic, a reputable-looking but
unconfirmed site.}
\end{figure}

>>>>

Only tried to connect directly (8/23): 
\begin{itemize}
\item E2-NEW-X21-20160323-1400
\item E2-OLD-X04-20160330-1800
\item E2-OLD-X10-20160331-1600
\item E3-NEW-X05-20160324-1400
\item E3-NEW-X17-20160323-1400
\item E3-OLD-X06-20160328-1400
\item E3-OLD-X06-20160330-1600
\item E3-OLD-X12-20160330-1800
\end{itemize}

Didn't know what to do next (6/23): 
\begin{itemize}
\item E3-NEW-X11-20160330-1600
\item E3-NEW-X11-20160331-1800
\item E3-NEW-X23-20160323-1400
\item E3-OLD-X06-20160331-1800
\item E3-OLD-X12-20160331-1600
\item E3-OLD-X30-20160328-1400
\end{itemize}

Thought that they needed a proxy (6/23): 
\begin{itemize}
\item E2-OLD-X10-20160328-1400
\item E3-NEW-X18-20160330-1800
\item E3-NEW-X17-20160328-1600
\item E3-OLD-X06-20160325-1800
\item E3-OLD-X06-20160330-1800
\item E3-OLD-X24-20160328-1600
\end{itemize}

Used the bridges auto-responder incorrectly (3/23): 
\begin{itemize}
\item E3-NEW-X23-20160328-1600 (Fig.~\ref{autoresponder1})
\item E3-OLD-X12-20160325-1400 (Fig.~\ref{autoresponder2})
\item E3-OLD-X24-20160328-1400 (Fig.~\ref{autoresponder3})
\end{itemize}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
\caption{The message that E3-NEW-X23-20160328-1600 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
\label{autoresponder1}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
\caption{The message that E3-OLD-X12-20160325-1400 accidentally sent to the helpdesk rather than the bridge auto-responder. The participant should have used the address bridges@torproject.org, not help@rt.torproject.org. Since the helpdesk address is not an auto-responder, there was no reply.}
\label{autoresponder2}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
\caption{The message that E3-OLD-X24-20160328-1400 sent to the bridge auto-responder. A correct message is a ``get bridges'' in the body of the message, with any non-empty subject. Since this request was incorrectly formatted, there was no reply.}
\label{autoresponder3}
\end{figure}

@@

Participants that downloaded Tor (5/124): 
\begin{itemize}
\item E1-OLD-X32-20160328-1400 (Fig.~\ref{mirror})
\item E2-NEW-X21-20160323-1400 (Fig.~\ref{techspot})
\item E2-OLD-X10-20160323-1400 (Fig.~\ref{downloadio})
\item E2-OLD-X28-20160328-1400 (Fig.~\ref{driverupdate})
\item E3-NEW-X11-20160330-1600 (Fig.~\ref{softsonic})
\end{itemize}

Sources of downloads: 
\begin{itemize}
\item {\bfseries techspot.com -> 1download.io:} the ad firefox yahoo ad result for ``tor browser downloads.'' 
\item {\bfseries driverupdate.net:} the 5th chrome google search result for ``tor browser download.'' 
\item {\bfseries www.torservers.net/mirrors:} the first chrome google search result for ``tor browser mirror.''
\item {\bfseries techspot.com:} the 5th chrome google search result for ``tor browser download.''
\item {\bfseries softsonic.com:} the 2nd firefox yahoo search result for ``tor browser.''
\end{itemize}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
\caption{E2-OLD-X10-20160323-1400 attempted downloaded Tor Browser from TechSpot.com, but clicked on one 
a download link which was not from TechSpot.com. The download was from 1download.io, a suspicious source.}
\label{downloadio}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
\caption{E2-OLD-X28-20160328-1400 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
participant dutifully does before running the Tor Browser executable.}
\label{driverupdate}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror,www.torservers.net/mirrors.}
\label{mirror}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
\caption{E2-NEW-X21-20160323-1400 downloaded Tor Browser from TechSpot, clicking on the download link from 
TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
\label{techspot}
\end{figure}

\begin{figure}[h]
\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
\caption{E3-NEW-X11-20160330-1600 downloaded Tor Browser from Softsonic, a reputable-looking but
unconfirmed site.}
\label{softsonic}
\end{figure}
